\begin{contributions}
%\begin{prefacesection}{Contribution of Authors}

	This thesis presents the work of six manuscripts.
	In each of these manuscripts, I was responsible for the software development,
	experimental design, model design, interpretation of results, and writing and editing of the manuscript.
	Co-authors of these papers were primarily involved in the conceptualisation of software, experimental design,
	reviewing of the manuscript and supervision. More specifically, author contributions are as follows.


	\textbf{Chapter~\ref{chp:bigdatastrategies}: Performance Evaluation of Big Data Processing Strategies for
Neuroimaging} \\
	I was responsible for the experimental and model design, implementation, evaluation and drafting of this paper.
	Shawn T. Brown was responsible for access to infrastructure and review and editing of the paper.
	Tristan Glatard provided supervision and aided with experimental and model design, and manuscript editing.


	\textbf{Chapter~\ref{chp:spa}: Evaluation of pilot jobs for Apache Spark applications on HPC
clusters} \\
	I was responsible for experimental and model design, software development, implementation of experiments,
	evaluation and the drafting of the manuscript. Tristan Glatard provided supervision, and aided with experimental and model design,
	and manuscript editing.

	\textbf{Chapter~\ref{chp:optane}: Performance benefits of
Intel\textsuperscript{\textregistered}~Optane\texttrademark~DC persistent memory
for the parallel processing of large neuroimaging data} \\
	I was responsible for the experimental and model design, implementation, evaluation and drafting of the manuscript.
	Shawn T. Brown was responsible for access to infrastructure and review and editing of the paper.
	Tristan Glatard provided supervision and aided with experimental and model design and implementation, and manuscript editing.

	\textbf{Chapter~\ref{chp:rp}: The benefits of prefetching for large-scale cloud-based neuroimaging
analysis workflows} \\
	I was responsible for the experimental and model design, implementation, evaluation and drafting of the manuscript.
	Tristan Glatard provided co-supervision and aided with experimental and model design, and manuscript editing.
	Ariel Rokem supervised the project, aided in experimental design, provided insight on diffusion MRI and reviewed and edited the manuscript.

	\textbf{Chapter~\ref{chapter:sea-comp}: Sea: A lightweight data-management library for Big Data scientific
computing}\\
	I was responsible for the software development, experimental and model design, evaluation and drafting of the manuscript.
	Tristan Glatard provided supervision and aided with experimental and model design, implementation of tests and manuscript editing.


	\textbf{Chapter~\ref{chapter:sea-neuro}: Automated neuroimaging data-management with Sea}\\
	I was responsible for the experimental and model design, implementation of experiments, evaluation and drafting of the manuscript.
	Tristan Glatard provided supervision, aided with experimental design and implementation and edited the manuscript.






%\end{prefacesection}
\end{contributions}